---
title: "Analyzing Yearly State Accidents Data"
author: "Yidan Cong"
date: "2018-08-26"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

This vignette provides usage details of the package AccData, which contains 
functions that access and extract information of accidents that have happened
in specific years.
In order for functions to work properly, please make sure that your data files
are in the same directory as `fars_function.R`.

`fars_read(filename)` takes in the filename of a csv file and returns a data 
frame containing the data object in the file. The function will terminate if 
the file defined by the `filename` does not exsit.

```{r}
fars_read("accident_2015.csv")
```

`make_filename(year)` is a helper function used in multiple functions in this package that returns a string of the filename defined by a specific year.

```{r}
make_filename("2014")
```

`fars_read_years(years)` returns a list of the MONTH and year column of accident
datasets.

`fars_summarize_years(years)` takes the list of MONTH and year columns returned by
the previous function and summarizes the number of accidents in each month and year.

`fars_map_state(state.num, year)` takes a state identification number `state.num` 
and a given year and returns a scatter plot of locations of accidents in that state. The x and y axes of the plot is defined by longitude and latitude of the 
location.

